Acceleration of Global Search by Implementing Dual Estimates for Lipschitz Constant\thanks{This research was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-09-11 2019/NUMTA_Barkalov/LNCS/numta19.tex
Four extra lines

Several typical methods of adaptive estimation of the Lipschitz constant are known:
\begin{itemize}
	\item global estimation of the constant $L$ in the whole search domain $D$ \cite{Horst1996,Pinter1996,Strongin2000}.
	\item local estimations of the constants $L_i$ in different subdomains $D_i$ of the search domain $D$ \cite{Kvasov2003,Sergeyev2010,Sergeyev2016}.
	\item the choice of the estimates of the constant $L$ from a set of possible values \cite{Gablonsky2001,Jones1993,Jones2009,Sergeyev2006}.
\end{itemize}

@@

%Russian
The new rules for finding the interval with the maximum characteristic will be as follows:
\begin{itemize}
\item 
Select the interval $(x_{t-1},x_t)$ corresponding to the maximum characteristic
\[
R(t)= \max_{1 \leq i \leq k}R(i).
\]
\item
Fix the value $r = r_{loc}$ if $\rho R_{loc}(t) > R_{glob}(t)$, otherwise fix $r=r_{glob}$.
\item
Use this value of $r$ in Rule 5 of the algorithm in the computing of the next trial point.
\end{itemize}

@@

Let the current minimum value of $z^*$ from (\ref{z}) be achieved at the left point of the $i^{\rm th}$ interval, i.e. $z^* = z_{i-1}$. 
As proven in \cite{Strongin2000}, according to the rule (\ref{R}) the following inequality will be true: 
\[
R(i) \geq \Delta_i \left( 1 - \frac{1}{r} \right)^2.
\]
Therefore, for the estimates of the characteristics $R_{loc}(i)$ and $R_{glob}(i)$ calculated with different parameters $r_{loc}$ and $r_{glob}$, the following relation will hold:
\[
	\Delta_i \left( 1 - \frac{1}{r_{glob}} \right)^2 > \Delta_i \left( 1 - \frac{1}{r_{loc}} \right)^2.
\]

>>>>

Several typical methods of adaptive estimation of the Lipschitz constant are known:
\begin{itemize}
	\item global estimation of the constant $L$ in the whole search domain $D$ \cite{Horst1996,Pinter1996,Strongin2000}.
	\item local estimations of the constants $L_i$ in different subdomains $D_i$ of the search domain $D$ \cite{Kvasov2003,Sergeyev2010,Sergeyev2016}.
	\item the choice of the estimates of the constant $L$ from a set of possible values \cite{Gablonsky2001,Jones1993,Sergeyev2006}.
\end{itemize}

@@

%Russian
The new rules for finding the interval with the maximum characteristic will be as follows:
\begin{itemize}
\item 
Select the interval $(x_{t-1},x_t)$ corresponding to the maximum characteristic $R(t)= \max_{1 \leq i \leq k}R(i)$.
\item
Fix the value $r = r_{loc}$ if $\rho R_{loc}(t) > R_{glob}(t)$, otherwise fix $r=r_{glob}$.
\item
Use this value of $r$ in Rule 5 of the algorithm in the computing of the next trial point.
\end{itemize}

@@

Let the current minimum value of $z^*$ from (\ref{z}) be achieved at the left point of the $i^{\rm th}$ interval, i.e. $z^* = z_{i-1}$. 
As proven in \cite{Strongin2000}, according to the rule (\ref{R}) the following inequality will be true: 
\[
R(i) \geq \Delta_i \left( 1 - 1/r \right)^2.
\]
Therefore, for the estimates of the characteristics $R_{loc}(i)$ and $R_{glob}(i)$ calculated with different parameters $r_{loc}$ and $r_{glob}$, the following relation will hold:
\[
	\Delta_i \left( 1 - 1/r_{glob} \right)^2 > \Delta_i \left( 1 - 1/r_{loc} \right)^2.
\]
